### 2023-10-17 ms.qmd
Adding some Bayesian code

pacman::p_load(tidyverse, flextable)
```

@@

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2)

@@

# Removing individuals who did not participate (more than 15 NAs)
data_associative <- data %>%
  group_by(lizard_id) %>%
  filter(sum(is.na(FC_associative)) <= 15) %>%
  ungroup()
data_associative <- as.data.frame(data_associative)

# Removing trials [36-40] (Only in associative)
data_associative <- data_associative %>%
group_by(lizard_id) %>%
filter(trial_associative <= 35) %>%
ungroup()
data_associative <- as.data.frame(data_associative)

@@

>>>>

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms)
```

@@

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo, lmerTest)

@@

# Removing individuals who did not participate (more than 15 NAs)
data_associative <- data %>%
  group_by(lizard_id) %>%
  filter(sum(is.na(FC_associative)) <= 15) %>%
  ungroup()  %>% data.frame()

# Removing trials [36-40] (Only in associative)
data_associative <- data_associative %>%
group_by(lizard_id) %>%
filter(trial_associative <= 35) %>%
ungroup()  %>% mutate(temp = gsub("[AB]_", "", trt),
                      cort = gsub("_[2][38]", "", trt))  %>% 
                mutate(group = factor(group, levels = c("R_B", "B_R"))) %>% data.frame()

@@

```{r, models}
#| label: dataclean
#| echo: false
#| warning: false

    null <- glmer(FC_associative ~ 1 + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))

GMM_deli2 <- glmer(FC_associative ~temp*cort*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
summary(GMM_deli2)

emmeans(GMM_deli2, pairwise ~ temp*Associative_Trial)
emmeans(GMM_deli2, pairwise ~ cort*Associative_Trial)

## Bayesian 
  mod <- brm(FC_associative ~ trt*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(mod)

# R2
bayes_R2(mod)

# Extract posteriors
posterior <- posterior_samples(mod, pars = "^b")
plyr::ldply(lapply(posterior, mean))
plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])

dharma(GMM_deli2)
install.packages("lmtest")
library(lmtest)
lrtest(null, GMM_deli)
anova(GMM_deli)
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group)) + labs(y = "Colour Association Task", x = "Trial")
print(plot_deli)
```
